\newpage
\subsection{Summary of the Results}
The first chapter of this thesis was all about the basics of Webdesign. Fundamentals like User
Interface Design, User Experience and Usability were researched and explained. Furthermore, the
world of Component Based UI Design with a focus of Atomic Design was introduced and recommended best
practices were shown.

The second chapter dealt with the topic of how web projects are usually developed and answers the
question of why traditional project management is not a suitable strategy for the majority of
software projects. It shows why Agile methods in combination with Lean UX can help mitigate
prevailing issues and how close collaboration between design and development can enhance the final
product. 

In the third chapter people and their experiences were in focus. A survey, with the goal of
uncovering major challenges of UI designers as well as engineers, was conducted and analyzed.
Discrepancies in the structure of UI components, lack of documentation, definition of edge cases and
misalignment in responsive design were found to be most severe issues.

With this strong foundation, the purpose of the fourth chapter was finding a solution to these
problems. By defining a vision that would guide the practical part of this paper, the project was
systematically built by identifying the needs and creating an idea, system and design language.
Guided by experiences from the survey content for seven distinct categories was curated and written.
To be sure, that the product can truly fulfill its vision, two additional interviews were performed
with the goal of uncovering even more issues as well as obtaining feedback to the status of the
practical project. 

With another iteration, the practical work was finished and presented in chapter five titled The
DesignAPI: A Shared Interface Between Design and Code. 